%-------------------------
% Resume in Latex
% Author : Alagappan P
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[most]{tcolorbox}
\input{glyphtounicode}

% Brand Colors (Emerald Cyber)
\definecolor{PrimaryEmerald}{HTML}{2ECC71}
\definecolor{AccentEmerald}{HTML}{10B981}
\definecolor{LightEmerald}{HTML}{E8F9F0}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting with icons
\newcommand{\sectionicon}[1]{\textcolor{PrimaryEmerald}{\faIcon{#1}}}

\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large\color{PrimaryEmerald}
}{}{0em}{}[\color{PrimaryEmerald}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape \color{AccentEmerald} Alagappan P} \\ \vspace{2pt}
    \small 
    \textcolor{AccentEmerald}{\faPhone\ } $|$ 
    \href{mailto:azhagu.swe@gmail.com}{\color{AccentEmerald}\faEnvelope\ azhagu.swe@gmail.com} $|$ 
    \href{https://linkedin.com/in/azhagu-swe/}{\color{AccentEmerald}\faLinkedin\ @azhagu-swe} $|$ 
    \href{https://github.com/azhagu-swe}{\color{AccentEmerald}\faGithub\ @azhagu-swe} $|$ 
    \href{https://azhagu-swe.github.io}{\color{AccentEmerald}\faGlobe\ azhagu-swe.github.io}
\end{center}

%-----------Summary-----------
\section{\faIcon{user-tie}\ Professional Summary}
\small{Full-stack Java Developer with \textbf{3.5+ years of experience} building scalable high-performance systems. Expert in \textbf{Spring Boot microservices, RESTful APIs, and PostgreSQL} optimization. Currently engineering secure banking solutions at \textbf{Infosys}, focusing on transaction efficiency, ACID compliance, and low-latency financial architecture. Proficient in AI-augmented development workflows to accelerate delivery and ensure high code quality.}

%-----------EXPERIENCE-----------
\section{\faIcon{briefcase}\ Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Infosys}{Nov 2025 \textendash\ Present}
      {Java Full Stack Developer (Banking Sector)}{Chennai, TN}
      \resumeItemListStart
        \resumeItem{Spearheading core \textbf{Banking microservices} development using Java 8+ and Spring Boot, focusing on transaction atomicity, multi-threading, and secure financial processing.}
        \resumeItem{Architecting high-throughput \textbf{RESTful APIs} designed for financial data integrity and sub-second response times in high-concurrency environments.}
        \resumeItem{Collaborating in an Agile squad to modernize legacy payment systems, utilizing \textbf{JFrog Artifactory} for secure binary management and \textbf{Splunk} for real-time monitoring and log analytics.}
        \resumeItem{Utilizing AI-augmented coding tools (\textbf{GitHub Copilot}) to streamline unit testing and achieve \textbf{80\%+} code coverage.}
      \resumeItemListEnd
      
    \resumeSubheading
      {MEmob Plus Pvt Ltd}{Aug 2022 \textendash\ Oct 2025}
      {Software Developer}{Chennai, TN}
      \resumeItemListStart
        \resumeItem{Optimized distributed microservices, achieving a \textbf{35\% reduction in API latency} through strategic Redis caching, SQL indexing, and query re-engineering.}
        \resumeItem{Architected a \textbf{unified audience management service} integrating Meta, Snapchat, and TikTok marketing APIs, processing millions of daily data points.}
        \resumeItem{Modernized legacy monolithic systems by re-architecting critical APIs into microservices, improving system scalability and user experience metrics by 20\%.}
        \resumeItem{Developed a specialized \textbf{proximity hash algorithm} in Java, significantly increasing location-targeting accuracy for geospatial marketing campaigns.}
        \resumeItem{Built high-performance dashboards with Next.js and React, improving Core Web Vitals and load times by 25\%.}
        \resumeItem{Established automated code quality gates using \textbf{SonarQube}, identifying and resolving 100+ critical vulnerabilities pre-production.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{\faIcon{microchip}\ Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{\color{PrimaryEmerald}Languages}{: Java, SQL, JavaScript, TypeScript, HTML, CSS} \\ \vspace{2pt}
     \textbf{\color{PrimaryEmerald}Backend}{: Spring Boot, Spring MVC, Hibernate, Microservices, RabbitMQ, Redis, REST APIs} \\ \vspace{2pt}
     \textbf{\color{PrimaryEmerald}Frontend}{: React.js, Next.js, Tailwind CSS, MUI, Shadcn UI, Mapbox} \\ \vspace{2pt}
     \textbf{\color{PrimaryEmerald}Tools \& Cloud}{: AWS, Docker, Git, SonarQube, Maven, JFrog, Splunk, GitHub Copilot}
    }}
 \end{itemize}

%-----------PROJECTS-----------
\section{\faIcon{code}\ Key Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{FarmConnect \textendash\ Agri-Commerce Platform} $|$ \emph{Spring Boot, PostgreSQL, React, AWS}}{2025}
          \resumeItemListStart
            \resumeItem{Architected a full-stack RBAC marketplace with 3 role types (Farmer/Buyer/Admin) and JWT authentication.}
            \resumeItem{Deployed on AWS EC2 via Docker Compose with search, filtering, and cart systems.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Developer Portfolio \& Blog} $|$ \emph{Next.js, TypeScript, Tailwind CSS, Velite, Framer Motion}}{2024 \textendash\ 2025}
          \resumeItemListStart
            \resumeItem{Engineered a high-performance, statically-generated portfolio using \textbf{Next.js App Router} and \textbf{TypeScript}, achieving a \textbf{97/100 Lighthouse score} and sub-second load times.}
            \resumeItem{Implemented a type-safe content layer with \textbf{Velite} for MDX-based blogging and project documentation, ensuring robust schema validation and optimized build-time performance.}
            \resumeItem{Designed a responsive, accessible UI with \textbf{Tailwind CSS} and \textbf{Framer Motion}, featuring dynamic theme switching and modern aesthetic micro-interactions.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{\faIcon{graduation-cap}\ Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {H.H. The Rajah's College}{Pudukottai, TN}
      {Master of Science (M.Sc) in Computer Science (74\%)}{2018 \textendash\ 2020}
    \resumeSubheading
      {H.H. The Rajah's College}{Pudukottai, TN}
      {Bachelor of Science (B.Sc) in Computer Science (71\%)}{2015 \textendash\ 2018}
  \resumeSubHeadingListEnd

%-----------AWARDS-----------
\section{\faIcon{trophy}\ Achievements \& Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Honors}{: Second Prize in National College Debugging Competition at Trichy.} \\
     \textbf{Certifications}{: Full Stack Java Development $|$ ChatGPT Advanced $|$ Prompt Engineering}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
